Supplementary Information 1

### 2025-04-01 index.Rmd
ggarrange plots

```{r}
SSplotTimeseries(base.model1.1,
                 subplot = 1)
SSplotTimeseries(base.model1.1,
                 subplot = 9)
SSplotTimeseries(base.model1.1,
                 subplot = 7)
```

@@

```{r}
SSplotTimeseries(base.model1.2,
                 subplot = 1)
SSplotTimeseries(base.model1.2,
                 subplot = 9)
SSplotTimeseries(base.model1.2,
                 subplot = 7)
```

@@

```{r}
SSplotTimeseries(base.model1.3,
                 subplot = 1)
SSplotTimeseries(base.model1.3,
                 subplot = 9)
SSplotTimeseries(base.model1.3,
                 subplot = 7)
```

@@

```{r}
SSplotTimeseries(base.model1.4,
                 subplot = 1)
SSplotTimeseries(base.model1.4,
                 subplot = 9)
SSplotTimeseries(base.model1.4,
                 subplot = 7)
```
Selectivity

```{r}
SSplotSelex(base.model1.1,
            subplots = 1)
SSplotSelex(base.model1.2,
            subplots = 1)
SSplotSelex(base.model1.3,
            subplots = 1)
SSplotSelex(base.model1.4,
            subplots = 1)
```

```{r}
SSplotIndices(base.model1.1,
            subplots = 9)
SSplotIndices(base.model1.2,
            subplots = 9)
SSplotIndices(base.model1.3,
            subplots = 9)
SSplotIndices(base.model1.4,
            subplots = 9)
```

@@

```{r}
SSplotRunstest(base.model1.1,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
SSplotRunstest(base.model1.2,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
SSplotRunstest(base.model1.3,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
SSplotRunstest(base.model1.4,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r}
SSplotRunstest(base.model1.1,
               subplots = "cpue",
               add=T,
               print = TRUE)
SSplotRunstest(base.model1.2,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1.3,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1.4,
               subplots = "cpue",
               add=T)
```

@@

```{r}
SSplotJABBAres(base.model1.1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.4,
               subplots = "len",
               add=T)
```

```{r}
SSplotJABBAres(base.model1.1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.4,
               subplots = "cpue",
               add=T)
```

@@

# Comparación con boxplot
boxplot(dfrmse, main = "RMSE comparision", col = c('#ca0020','#f4a582','#bababa','#404040'))

# Prueba de diferencias estadísticas (ANOVA)
anova_result <- aov(as.numeric(unlist(dfrmse)) ~ rep(1:4, each=nrow(dfrmse)))
summary(anova_result)

@@

dfrmse_long <- reshape2::melt(dfrmse)

ggplot(dfrmse_long, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot(width=0.3) +
  geom_jitter(width = 0.01, alpha = 0.3) +
  theme_minimal() +
  scale_fill_manual(name= "Scenario",
                    values = c("Model1.1" = "#ca0020", 
                               "Model1.2" = "#f4a582", 
                               "Model1.3" = "#bababa", 
                               "Model1.4" = "#404040")) +
  labs(title = "", x = "", y = "RMSE")

```
This boxplot compares a summary of the Root Mean Square Error (RMSE) across four different models (s1.1, s1.2, s1.3, and s1.4) used to evaluate recruitment estimates of Antarctic krill. RMSE serves as an indicator of model accuracy, with lower values representing better predictive performance.

@@

```{r}
#save(retroSummary, retroModels, file="retro5.Rdata")
retro1.1 <- SSplotRetro(retroSummary1.1,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
retro1.2 <- SSplotRetro(retroSummary1.2,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
retro1.3 <- SSplotRetro(retroSummary1.3,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
retro1.4 <- SSplotRetro(retroSummary1.4,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
```

@@

```{r}
hci = SSplotHCxval(retroSummary1.1, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary1.2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary1.3, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary1.4, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7) 
```

@@

# Combine the results from all models into one table
tablebias_combined <- bind_rows(
  data.frame(Model = "s1.1", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.1", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.4", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.4",
             Quant = "F", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "F", verbose = F))
)

kbl(tablebias_combined, booktabs = T, 
    format = "html", 
    caption = "Rho parameter by model and quantity (SSB and F)") %>% 
  kable_styling(latex_options = "HOLD_position")

@@

```{r fig.width=5, fig.height=7}
recs1 <- base.model1.1$recruit$pred_recr
recs2 <- base.model1.2$recruit$pred_recr
recs3 <- base.model1.3$recruit$pred_recr
recs4 <- base.model1.4$recruit$pred_recr

@@

ggarrange(p1,
          p2,
          p3,
          p4, ncol=1, nrow = 4,
          common.legend = T)

@@

```{r fig.width=5, fig.height=7}
dev1 <- base.model1.1$recruit[8:35,c(1,7)]%>% 
  mutate(Serie = "s1.1")
dev2 <- base.model1.2$recruit[8:35,c(1,7)] %>% 
  mutate(Serie = "s1.2")
dev3 <- base.model1.3$recruit[8:35,c(1,7)] %>% 
  mutate(Serie = "s1.3")
dev4 <- base.model1.4$recruit[8:35,c(1,7)] %>% 
  mutate(Serie = "s1.4")

@@

# Organizar los gráficos con ggarrange
combined_plot <- ggarrange(plotlist = plots, ncol = 1, nrow = 4)

>>>>

par(mfrow=c(1,3), mar=c(5,4,1,1)) 
SSplotTimeseries(base.model1.1,
                 subplot = 1)
SSplotTimeseries(base.model1.1,
                 subplot = 9)
SSplotTimeseries(base.model1.1,
                 subplot = 7)
```

@@

```{r}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.2,
                 subplot = 1)
SSplotTimeseries(base.model1.2,
                 subplot = 9)
SSplotTimeseries(base.model1.2,
                 subplot = 7)
```

@@

```{r}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.3,
                 subplot = 1)
SSplotTimeseries(base.model1.3,
                 subplot = 9)
SSplotTimeseries(base.model1.3,
                 subplot = 7)
```

@@

```{r}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.4,
                 subplot = 1)
SSplotTimeseries(base.model1.4,
                 subplot = 9)
SSplotTimeseries(base.model1.4,
                 subplot = 7)
```
Selectivity

```{r}
par(mfrow=c(2,2), mar=c(5,4,1,1))
SSplotSelex(base.model1.1,
            subplots = 1)
mtext("s1.1", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.2,
            subplots = 1)
mtext("s1.2", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.3,
            subplots = 1)
mtext("s1.3", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.4,
            subplots = 1)
mtext("s1.4", side=3, line=0.5, cex=1.2)
```

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))

SSplotIndices(base.model1.1, subplots = 9)
mtext("s1.1", side=3, line=0.5, cex=1.2)

SSplotIndices(base.model1.2, subplots = 9)
mtext("s1.2", side=3, line=0.5, cex=1.2)

SSplotIndices(base.model1.3, subplots = 9)
mtext("s1.3", side=3, line=0.5, cex=1.2)

SSplotIndices(base.model1.4, subplots = 9)
mtext("s1.4", side=3, line=0.5, cex=1.2)

@@

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1)) 
SSplotRunstest(base.model1.1,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
SSplotRunstest(base.model1.2,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
SSplotRunstest(base.model1.3,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
SSplotRunstest(base.model1.4,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r eval=FALSE}
SSplotRunstest(base.model1.1,
               subplots = "cpue",
               add=T,
               print = TRUE)
SSplotRunstest(base.model1.2,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1.3,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1.4,
               subplots = "cpue",
               add=T)
```

@@

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))
SSplotJABBAres(base.model1.1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.4,
               subplots = "len",
               add=T)
```

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))
SSplotJABBAres(base.model1.1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.4,
               subplots = "cpue",
               add=T)
```

@@

@@

dfrmse_long <- reshape2::melt(dfrmse)
ggplot(dfrmse_long, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot(width=0.3) +
  geom_jitter(width = 0.01, alpha = 0.3) +
  theme_minimal() +
  scale_fill_manual(name= "Scenario",
                    values = c("Model1.1" = "#ca0020", 
                               "Model1.2" = "#f4a582", 
                               "Model1.3" = "#bababa", 
                               "Model1.4" = "#404040")) +
  labs(title = "", x = "", y = "RMSE")
```
This boxplot compares a summary of the Root Mean Square Error (RMSE) across four different models (s1.1, s1.2, s1.3, and s1.4) used to evaluate recruitment estimates of Antarctic krill. RMSE serves as an indicator of model accuracy, with lower values representing better predictive performance.

@@

par(mfrow=c(2,2), mar=c(5,4,1,1))

retro1.1 <- SSplotRetro(retroSummary1.1,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
retro1.2 <- SSplotRetro(retroSummary1.2,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
retro1.3 <- SSplotRetro(retroSummary1.3,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
retro1.4 <- SSplotRetro(retroSummary1.4,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("SSB"))
```
```{r}

par(mfrow=c(2,2), mar=c(5,4,1,1))

retro1.1 <- SSplotRetro(retroSummary1.1,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("F"))
retro1.2 <- SSplotRetro(retroSummary1.2,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("F"))
retro1.3 <- SSplotRetro(retroSummary1.3,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("F"))
retro1.4 <- SSplotRetro(retroSummary1.4,
            add=T,
            forecast = F,
            legend = T,
            verbose=F,
            subplots = c("F"))
```

@@

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.1, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.3, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.4, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7) 
```

@@

# Combine the results from all models into one table
tablebias_combined <- bind_rows(
  data.frame(Model = "s1.1", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.1", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.4", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.4",
             Quant = "F", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "F", verbose = F))
)
```

```{r}
kbl(tablebias_combined, booktabs = T, 
    format = "html", 
    caption = "Rho parameter by model and quantity (SSB and F)") %>% 
  kable_styling(latex_options = "HOLD_position")

@@

```{r}
recs1 <- base.model1.1$recruit$pred_recr
recs2 <- base.model1.2$recruit$pred_recr
recs3 <- base.model1.3$recruit$pred_recr
recs4 <- base.model1.4$recruit$pred_recr

@@

ggarrange(p1,
          p2,
          p3,
          p4, ncol=2, nrow = 2,
          common.legend = T)

@@

```{r, warning=FALSE}
dev1 <- base.model1.1$recruit[8:35,c(1,7)]%>% 
  mutate(Serie = "s1.1")
dev2 <- base.model1.2$recruit[8:35,c(1,7)] %>% 
  mutate(Serie = "s1.2")
dev3 <- base.model1.3$recruit[8:35,c(1,7)] %>% 
  mutate(Serie = "s1.3")
dev4 <- base.model1.4$recruit[8:35,c(1,7)] %>% 
  mutate(Serie = "s1.4")

@@

# Organizar los gráficos con ggarrange
combined_plot <- ggarrange(plotlist = plots, ncol = 2, nrow = 2)
